Voter Characteristics and Political Support in the US

### 2024-03-12 paper/paper.qmd
Add paragraphs to model justification section

## Model justification

>>>>

## Model justification
[Paragraph 1: How features enter the model and why → link with data section]

We chose gender, race, and gun ownership status to be the predictor variables in our model. These features were chosen based on our data section. [more explanation] First, we expect a negative relationship between men and support for Biden. [more explanation] Second, we expect a positive relationship between non-white respondents and support for Biden. [more explanation] Third, we expect a negative relationship between gun owners and support for Biden. [more explanation]

[Paragraph 2: Assumptions that underpin the model]

Logistic regression does not make the same assumptions as linear regression. First, linear regression assumes a continuous outcome variable that can take any number on the real line, whereas logistic regression assumes a binary outcome variable. Furthermore, linear regression requires that the outcome variable is a linear function of the predictor variables, while the outcome in logistic regression is part of the exponential family. However, logistic regression does assume that the relationship between the log-odds of the binary outcome and predictor variables is linear. Lastly, unlike in linear regression, logistic regression does not require the assumption of homoscedasticity of errors.

[Paragraph 3: Alternative models or variants; Strengths and weaknesses; Circumstances in which the model may not be appropriate]

Alternative regression models were considered, but rejected because they were not appropriate for our outcome variable. Linear models assume a continuous outcome variable, and Poisson and Negative binomial models assume count outcome variables. Since our outcome variable is binary, we chose to use logistic regression.

[Paragraph 4: Evidence of model validation and checking, model convergence, and/or diagnostic issues]
